replication_report

### 2015-03-31 replication_report.Rmd
attempt to clean up

#load data:
dat <- read.csv("GORN_study3.csv", header = TRUE)
head(dat)
View(dat)

@@

```

@@

```{r, echo=FALSE}
##Scatterplots
graph.simple = ggplot(dat, aes(x = wmc.center, y = stroop.rt)) 
graph.simple + geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("Simple Effect of Working Memory on Stroop Performance (RT)") +
  ylab("Stroop RT") +
  xlab("Working Memory Deviation Score from Mean")

graph.moderator = ggplot(dat, aes(x = X.center, y = Y, colour = M)) 
graph.moderator + geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("Working Memory on Stroop Performance (RT)") +
  ylab("Stroop RT") +
  xlab("Working Memory Deviation Score from Mean")
```

>>>>

#load data:
dat <- read.csv("GORN_study3.csv", header = TRUE)
dat <-tbl_df(dat)
View(dat)
dat %>%
  filter(na.rm=TRUE) %>%
  group_by(Groep) %>%
  summarise(total.n = n())

by_group<-group_by(dat, Groep)
mutate(distinct_groups= count(n_distinct(Groep))
summarise(distinct_groups)
count(dat, distinct_groups(N()))

#Frequencies of each group:
ddply(dat,.(Groep),
      summarise,
      count = length(form_nr1)
      )

@@

#Work on tables:
#In another working document (because incomplete)
```

@@

```{r, echo=FALSE}
##Scatterplots for add on to study graphs 
graph.simple = ggplot(dat, aes(x = , y = )) 
graph.simple + geom_smooth(method = "") +
  geom_point() +
  ggtitle("") +
  ylab("") +
  xlab("")

graph.moderator = ggplot(dat, aes(x = X.center, y = Y, colour = M)) 
graph.moderator + geom_smooth(method = "lm") +
  geom_point() +
  ggtitle("") +
  ylab("") +
  xlab("")
```
